### 2015-06-01 writing/SNLI paper/entailment_eval.tex
Minor changes

%
% EOP
%
\paragraph{Excitement Open Platform}
% what is EOP
The Excitement Open Platform is a tool to quickly develop NLI systems
  while sharing components such as common lexical resources and 
  evaluation sets.
We evaluate against three algorithms included in the distribution,
  and also evaluated in \newcite{magnini2014excitement}.
These are: 
  (1) a simple edit-distance based algorithm; and
  (2) a classifier-based algorithm.
%  (3) an algorithm based around tree transformations.

@@

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\b{System} & \b{Our corpus} & \b{SICK} & \b{RTE-3} \\
\midrule
\t{Edit Distance Based}        & \t{71.9} & \t{65.4} & \b{61.9} \\
\t{Classifier Based}           & \b{72.2} & \b{71.4} & \t{61.5} \\
%\midrule
%\t{Classifier Based (3-class)} & \t{??.?} & \t{65.6} & \t{} \\
%\t{Transformation Based} & \t{36.0} & \t{76.7} & \t{56.4} \\  % broken! At least, on SNLI...
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
2-class test accuracy for two systems included in the
  Excitement Open Platform.
%All RTE results are 2-class accuracy.
%The transformation-based model allows for 3-class predictions on our
%  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c}
\toprule
\b{System}	 & \multicolumn{2}{c}{\hspace{-1.2em}\b{Our corpus}} & \b{SICK}\\
 & \t{Train} & \t{Test} & \t{Test}\\
\midrule
\t{Lexicalized}            & \t{99.7}  & \b{78.2} & \b{77.3} \\ % & \t{78.7}
\t{Unigrams Only}          & \t{93.1} & \t{71.6} & \t{74.0} \\ % & \t{72.2}
\t{Unlexicalized}          & \t{49.4} & \t{50.4} & \t{69.4}\\ % & \t{50.1} % Last value was 50.39; rounded for consistency.
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
3-class accuracy, training and testing on either our data or SICK, including models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
}
\end{table}
%
% END BOW RESULTS TABLE
%

% Results
We report results in \reftab{tab:bowresults}, along with ablation studies for removing
  the cross-bigram features (leaving only the cross-unigram feature),
  and for removing all lexicalized features.
% Insights 1: lexicalization helps a bunch
On our large corpus in particular, there is a substantial jump in accuracy from using
  lexicalized features, and another from using the very sparse
  cross-bigram features.
The latter  result can be explained if
  the classifier automatically learns to recognize explicit negations and adjective
  modification, and a similar result was shown in
  \newcite{sidaw12simple} for bigram features in sentiment analysis.

@@

>>>>

%
% EOP
%
\paragraph{Excitement Open Platform}
% what is EOP
The Excitement Open Platform is a tool to quickly develop NLI systems
  while sharing components such as common lexical resources and 
  evaluation sets.
We evaluate against two algorithms included in the distribution,
  and also evaluated in \newcite{magnini2014excitement}.
These are: 
  a simple edit-distance based algorithm; and
  a classifier-based algorithm.
%  (3) an algorithm based around tree transformations.

@@

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\toprule
\b{System} & \b{Our corpus} & \b{SICK} & \b{RTE-3} \\
\midrule
\t{Edit Distance Based}        & \t{71.9} & \t{65.4} & \b{61.9} \\
\t{Classifier Based}           & \b{72.2} & \b{71.4} & \t{61.5} \\
%\midrule
%\t{Classifier Based (3-class)} & \t{??.?} & \t{65.6} & \t{} \\
%\t{Transformation Based} & \t{36.0} & \t{76.7} & \t{56.4} \\  % broken! At least, on SNLI...
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
2-class accuracy for two entailment algorithms included in the
  Excitement Open Platform.
%All RTE results are 2-class accuracy.
%The transformation-based model allows for 3-class predictions on our
%  corpus and SICK; these are reported in the last row.
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

% The table
\begin{table}
\begin{center}
\def\t#1{\small{#1}}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c}
\toprule
\b{System}	 & \multicolumn{2}{c}{\hspace{-1.2em}\b{Our corpus}} & \b{SICK}\vspace{-0.5mm}\\
 & \t{Train} & \t{Test} & \t{Test} \vspace{-0.5mm}\\
\midrule
\t{Lexicalized}            & \t{99.7}  & \b{78.2} & \b{77.3} \\ % & \t{78.7}
\t{Unigrams Only}          & \t{93.1} & \t{71.6} & \t{74.0} \\ % & \t{72.2}
\t{Unlexicalized}          & \t{49.4} & \t{50.4} & \t{69.4}\\ % & \t{50.1} % Last value was 50.39; rounded for consistency.
\bottomrule
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:bowresults}
3-class accuracy, training and testing on either our data or SICK, including models lacking cross-bigram features 
  (Feature \ref{lst:bigram}), and lacking all lexical
  features (Features \ref{lst:ngram}--\ref{lst:bigram}).
}
\end{table}
%
% END BOW RESULTS TABLE
%

% Results
We report results in \reftab{tab:bowresults}, along with ablation studies for removing
  the cross-bigram features (leaving only the cross-unigram feature),
  and for removing all lexicalized features.
% Insights 1: lexicalization helps a bunch
There is a substantial jump in accuracy from using
  lexicalized features, and even from using the relatively sparse
  cross-bigram features.
The latter of these was initially surprising, but can be explained if
  the classifier automatically learns to recognize explicit negations and adjective
  modification---such a result was shown in
  \newcite{sidaw12simple} for bigram features in sentiment analysis.

@@

training sets
